Scan-Centric, Frequency-Based Method for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-30 doc/peakcharacterization_manuscript.Rmd
more styling

## Discussion

## Materials and Methods

@@

$$mz = intercept + x* \frac{1}{frequency} + y*\frac{1}{frequency^2} + z*\frac{1}{frequency^3}$$

@@

@@

For each raw data file in profile mzML format, they were processed in these six ways:

1.  No noise removal, no normalization, no frequency SD filtering (noperc_nonorm)
2.  Noise removal, no normalization, no frequency SD filtering (perc99_nonorm)
3.  Noise removal, single pass normalization with all peaks, no frequency SD filtering (singlenorm)
4.  Noise removal, single pass normalization with high ratio peaks, no frequency SD filtering (singlenorm_int)
5.  Noise removal, two pass normalization, no frequency SD filtering (doublenorm)
6.  Noise removal, two pass normalization, frequency SD filtering (filtersd)
7.  Scan level peak centroids generated by MSnbase (using `pickPeaks` on the individual scans)
8.  Scans merged and then centroids generated by MSnbase (using `combineSpectra` and `pickPeaks`)

For the two sets of MSnbase peaks, we also matched scan level peaks to merged peaks via two methods:

1.  All scan level peaks within a 2ppm window are associated with the *merged* peak
2.  Using the *filtersd* peaks, merged and scan level peaks are associated if they are within the start and stop m/z of the *filtersd* peaks

## Conclusions

## References

>>>>

::: {custom-style="MDPI_2.1_heading1"}
## Discussion
:::

::: {custom-style="MDPI_3.1_text"}
we should have some discussion here about the results
:::

::: {custom-style="MDPI_2.1_heading1"}
## Materials and Methods
:::

@@

::: {custom-style="MDPI_3.9_equation"}
$$mz = intercept + x* \frac{1}{frequency} + y*\frac{1}{frequency^2} + z*\frac{1}{frequency^3}$$
:::

@@

::: {custom-style="MDPI_2.2_heading2"}
### Assigning Scan-Centric Peaks
:::

We created potential EMF databases for SMIRFE assignments for ECF and 15N labeled amino acids or for lipids (see supplemental materials for the actual limits).
We assigned ECF derivatized amino acid samples with 15N labeling, a single positive charge, and H and Na as adducts.
We assigned lipid samples with no labeling, a single positive charge, and H, Na, K, and NH4 as possible adducts.
We attempted to create peaks that could be assigned by SMIRFE from the MSnbase and Xcalibur peak lists, but SMIRFE would not assign them.

::: {custom-style="MDPI_2.2_heading2"}
### Matching Peaks
:::

We matched the scan-centric peaks to the other methods by looking for the closest m/z peak that was within 2 ppm of the scan-centric reported m/z.

::: {custom-style="MDPI_2.2_heading2"}
### Peak - Peak NAP Height Ratios
:::

@@

::: {custom-style="MDPI_3.5_text_before_list"}
For each raw data file in profile mzML format, they were processed in these six ways:
:::

::: {custom-style="MDPI_3.8_bullet"}
* No noise removal, no normalization, no frequency SD filtering (noperc_nonorm)
:::
::: {custom-style="MDPI_3.8_bullet"}
* Noise removal, no normalization, no frequency SD filtering (perc99_nonorm)
:::
::: {custom-style="MDPI_3.8_bullet"}
* Noise removal, single pass normalization with all peaks, no frequency SD filtering (singlenorm)
:::
::: {custom-style="MDPI_3.8_bullet"}
* Noise removal, single pass normalization with high ratio peaks, no frequency SD filtering (singlenorm_int)
:::
::: {custom-style="MDPI_3.8_bullet"}
* Noise removal, two pass normalization, no frequency SD filtering (doublenorm)
:::
::: {custom-style="MDPI_3.8_bullet"}
* Noise removal, two pass normalization, frequency SD filtering (filtersd)
:::
::: {custom-style="MDPI_3.8_bullet"}
* Scan level peak centroids generated by MSnbase (using `pickPeaks` on the individual scans)
:::
::: {custom-style="MDPI_3.8_bullet"}
* Scans merged and then centroids generated by MSnbase (using `combineSpectra` and `pickPeaks`)
:::

::: {custom-style="MDPI_3.5_text_before_list"}
For the two sets of MSnbase peaks, we also matched scan level peaks to merged peaks via two methods:
:::

::: {custom-style="MDPI_3.8_bullet"}
* All scan level peaks within a 2ppm window are associated with the *merged* peak
:::

::: {custom-style="MDPI_3.8_bullet"}
* Using the *filtersd* peaks, merged and scan level peaks are associated if they are within the start and stop m/z of the *filtersd* peaks
:::

::: {custom-style="MDPI_2.1_heading1"}
## Conclusions
:::

::: {custom-style="MDPI_2.1_heading1"}
## References
:::
